Starspots on sub sub giants

### 2019-12-04 document/ms.tex
Remove placeholder text
Add prose describing the K2 FFI zero-point calibration.

We do not know what causes some sub-sub giants!
But now we know a little... more. Hence this paper!

@@

\begin{figure*}[hbt!]
  \centering
  \begin{tabular}{ccccc}
    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_PS1_g.png}} &
    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_2M_J.png}} &
    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_K2_C5.png}} &
    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_K2_C16.png}} &
    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_K2_C18.png}} \\
  \end{tabular}
\caption{Imaging of S1063 in $60'' \times 60''$ postage stamps. \emph{left-to-right:} Pan-STARRS $g$-band co-added image contemporaneous with C16; 2MASS $J-$band; K2 Campaigns 5, 16, 18.}
\label{fig:imaging}
\end{figure*}

@@

>>>>

@@

\begin{figure*}[hbt!]
  \centering
  \begin{tabular}{ccccc}
    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_PS1_g.png}} &
    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_2M_J.png}} &
    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_K2_C5.png}} &
    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_K2_C16.png}} &
    \subfloat{\includegraphics[width=1in]{figures/S1063_60x60arcsec_K2_C18.png}} \\
  \end{tabular}
\caption{Imaging of S1063 in $60'' \times 60''$ postage stamps. \emph{left-to-right:} Pan-STARRS $g$-band co-added image contemporaneous with C16; 2MASS $J-$band; K2 Campaigns 5, 16, 18 from Full Frame Images.  S1063 is sufficiently separated from nearby sources in the coarse \emph{Kepler} imaging.}
\label{fig:imaging}
\end{figure*}

@@

\subsection{Inter-campaign relative photometry with K2 Full Frame Images}

Stellar activity cycles on S1063 can secularly change the stellar brightness on timescales comparable to the separation of the three campaigns of \emph{K2} observations.  The comparison of flux levels among repeated \emph{K2} campaigns requires accounting for detector responsivity degradation on these same timescales.  The absolute sensitivity of the \emph{Kepler} detector pixels decay at $XX \%\;yr^{-1}$ due to sudden pixel sensitivity dropouts and other environmental lifetime factors (CITE Caldwell,Montet).  We calibrated the system-integrated throughput for \emph{Kepler} detector channels possessing the M67 field in campaigns 5, 16, and 18.  We measured aperture photometry for about two thousand isolated reference stars using the Full Frame Images (FFIs), keeping only reference stars that had repeated observations in all three campaigns.  Campaign 16 reference stars had a median flux of $93.9\pm4.2\%$ relative to campaign 5; campaign 18 showed $98.2\pm2.8\%$ relative to campaign 5.  These flux ratios dictate the vertical registration of the \emph{K2} lightcurves in Figure XX.
